A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-04-12 manuscript.Rmd

---
title: "A Hitchhiker's Guide to Reproducible Research" # replace with something serious
output: bookdown::pdf_document2
repro:
  packages:
    - usethis
    - aaronpeikert/repro@7bfaf98
    - here
    - rstudio/webshot2@f62e743
csl: apa7.csl
numbered_headings: true
toc_depth: 5
bibliography: references.bib
---

@@

```{r schematic, eval = TRUE, echo = FALSE, fig.cap="Schematic illustration of the interplay of the four components (in dashed boxes) central to the reproducible workflow: version control (Git), dependency tracking (Make), software management (Docker), and dynamic document generation (R Markdown). Git tracks changes to the project over time. Make manages dependencies among the files. Docker provides a container in which the final report is built using dynamic document generation in R Markdown. Reproduced from @Peikert2019.  "}
# file gets downloaded in Makefile
knitr::include_graphics("images/nutshell.svg", auto_pdf = TRUE)
```

@@

There are probably few things as frustrating as realizing that the data that you gathered cannot answer the research question you had in mind.
A step to prevent unpleasant surprises is to simulate data.
Simulated data lets you verify that the data you expect to gather and the analysis that you plan fit together.

>>>>

---
title: "A Hitchhiker's Guide to Reproducible Research" # replace with something serious
output: bookdown::pdf_document2
repro:
  packages:
    - usethis
    - aaronpeikert/repro@7bfaf98
    - here
    - rstudio/webshot2@f62e743
  scripts:
    - R/lavaan_helper.R
    - R/simulation.R
    - R/link.R
csl: apa7.csl
numbered_headings: true
bibliography: ["references.bib", "packages.bib"]
---

@@

```{r schematic, eval = TRUE, echo = FALSE, fig.cap="Schematic illustration of the interplay of the four components (in dashed boxes) central to the reproducible workflow: version control (Git), dependency management (Make), software management (Docker), and dynamic document generation (R Markdown). Git tracks changes to the project over time. Make manages dependencies among the files. Docker provides a container in which the final report is built using dynamic document generation in R Markdown. Reproduced from @Peikert2019.  "}
# file gets downloaded in Makefile
knitr::include_graphics("images/nutshell.svg", auto_pdf = TRUE)
```

@@

```{r, include=FALSE}
source(here::here("R", "simulation.R"))
```

There are probably few things as frustrating as realizing that the data that you gathered cannot answer the research question you had in mind.
A step to prevent unpleasant surprises is to simulate data.
Simulated data lets you verify that the data you expect to gather and the analysis you plan fit together.
Of course, one has to make many educated guesses to simulate data that closely matches your expectation.
These guesses strongly depend on the study you are planning, and there cannot be a one fits all solution.
However, the analytic strategy often gives you a hint about how to simulate data.
In the Machiavellism example, the analytic strategy is to use structural equation modelling (SEM).
To simulate data for SEM, one has to specify a model and then sample from a multivariate normal distribution following its implied covariance matrix.
The model parameters should mimic the Machiavellism subscale of the short dark triad (SD3).
As a starting point, we can use already published information.
@Jones2013 report loadings seen in Table \@ref(tab:loadings) and report a gender difference (at the manifest level) depending on the sample between `r min(cohend_jones_paulhus)` and `r max(cohend_jones_paulhus)`.

```{r loadings, echo=FALSE}
knitr::kable(data.frame(Item = 1:9,
                        Loading = loadings_jones_paulhus),
             caption = "Factor loadings from an Exploratory Structrural Equation Model as reported in Jones \\& Paulhus (2013)")
```

It is probably better to assume more pessimistic values.
This way, we make sure that our analytic strategy is viable even in non-optimal circumstances.
Therefore, we will assume that the loadings are 30% lower than reported and that the standardized mean difference is only 0.1.
These assumption can be simply translated into [`lavaan` [@lavaan]](https://lavaan.ugent.be)[^lavaan] model syntax:

[^lavaan]: https://lavaan.ugent.be

```{r, results='asis', echo=FALSE}
model_truth <- combine(
  measurement(
    "MACH",
    items("x", 9),
    loadings = round(loadings_jones_paulhus * 0.7, 2)
    ),
  intercepts("MACH", list(0, 0.1))
  )
cat("``` r",
    model_truth,
    "```",
    sep = "\n")
model <- combine(measurement(
  "MACH",
  items("x", 9)),
  intercepts("MACH", list(0, "NA")))
```

From which we can simulate data:

```{r, results='hide'}
simulated <- lavaan::simulateData(
  model_truth,
  sample.nobs = c(1000, 1000),
  meanstructure = TRUE,
  standardized = TRUE
)
```

And then fit the statistical model:

```{r}
fit <-
  lavaan::cfa(
    model,
    data = simulated,
    group = "group",
    meanstructure = TRUE,
    std.lv = TRUE
  ) 
```

But wait `lavaan` warns us that this model may not be identified.
We overlooked a crucial assumption of this model, that is measurement invariance.
This assumption is also baked into our simulation of the data.
It is probably more realistic to violate this assumption and plan our analysis accordingly.
Therefore, we simulate the data so that some of the items parameter differ among groups and then alter the analysis to assume partial measurement invariance.
While reconsidering our assumptions, it is also unlikely that the data is normally distributed.
Not only would the actual items be Likert-like and therefore categorical, but also are the in @Jones2013 reported means not in the middle of the scale, thus suggesting some skewness to the items.
@Rhemtulla2012 conclude that using Likert-like items is acceptable when they employ five or more categories.
Hence, we continue simulating continues data.
However, adding a little skewness to the items is easy and helps make the simulation more realistic.
Anyhow, remember that what we consider realistic for our case could be unfit for your case.
If you are satisfied with your assumptions it helps to write a function that expresses them, like this one:
<!--Hands-on: build simple functions tailored for your analysis-->

```{r generate}
```

Note however that this function is again composed of several functions, which you may inspect on `r link("https://github.com/aaronpeikert/repro-tutorial/blob/master/R/simulation.R", "GitHub")`.

With its help we can simulate 500 cases with a mean difference between groups of 0.1, where the intercepts of three random items vary by .3 and three loadings vary by 30% and five random items have a skew.

```{r}
simulated <- generate(n = 500,
                      diff = 0.1,
                      vary_intercepts = rep(0.3, 3),
                      vary_loadings = rep(0.3, 3),
                      skewness = rep(5, -0.5))
```

Note, that this certainly results in different numbers each time we run it.
To consistently get the same results it is good practice to use a seed.
The function `seeded_generate()` will always generate the same pseudo-random numbers, when given the same seed.

```{r}
seeded_generate <-  function(seed, ...)withr::with_seed(seed, generate(...))
simulated <- seeded_generate(
  seed = 1234,
  n = 100000,
  diff = 0.1,
  vary_intercepts = rep(0.3, 3),
  vary_loadings = rep(0.3, 3),
  skewness = rep(5,-0.5)
)
```

```{r}
lavaan::summary(analyze(simulated))
```

### Preregestration (optional)
